---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# energizer

<!-- badges: start -->
[![R-CMD-check](https://github.com/gggiraldo/enrgz/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/gggiraldo/enrgz/actions/workflows/R-CMD-check.yaml)
[![Codecov test coverage](https://codecov.io/gh/gggiraldo/enrgz/graph/badge.svg)](https://app.codecov.io/gh/gggiraldo/enrgz)
<!-- badges: end -->

R Interface to get EPC data using the OpenDataCommunities API

## Installation

You can install the development version of energizer from [GitHub](https://github.com/) with:

```{r, eval = FALSE}
# install.packages("pak")
pak::pak("gggiraldo/energizer")
```

or with: 

```{r, eval = FALSE}
remotes::install_github("gggiraldo/energizer")
```

## Getting the API key

To get the API key, visit the [opc.opendatacommunities.org](https://epc.opendatacommunities.org/#register) website.

A confirmation containing the API key will be sent to the e-mail address provided during registration.

## 🪪 API Credentials Setup

First, to start using `energizer` you need to set your API key with: 

```{r, eval = FALSE}
energizer::odc_set_key(
  odc_user = "username", 
  odc_key = "api-key"
)
```

where `odc_user` is the address provided during the registration process, and `odc_key` is the one included in the confirmation e-mail.

## 🔍 General Search

The `search_domestic` function allows to search for certificates using various filters:

```{r, include = FALSE, echo = FALSE}
Sys.unsetenv("ODC_API_KEY") 
energizer::odc_set_key(
  Sys.getenv("ODC_USERNAME"),
  Sys.getenv("ODC_PW") 
)
```

```{r, message = FALSE, warning = FALSE}
energizer::odc_search_data(
  address = "liverpool road",
  type = "domestic"
)
```

By default, the function returns 25 records matching the filtering criteria. This behavior can be changed using the `max_records` parameter: 

```{r, , message = FALSE, warning = FALSE}
london_search_50 <- 
  energizer::odc_search_data(
    address = "liverpool road",
    type = "domestic",
    max_records = 50
  )

dim(london_search_50)
```

## 🔑 `lmk_key`-based Search 

Certitificates can also be retrieved using the `lmk_key` field attribute, representing the "*Individual lodgement identifier*", which is unique and "*[...]can be used to identify a certificate*".

```{r, include = FALSE, echo = FALSE}
domestic_lmk_key <- "00031a8942cc0091d033fbe4ba1c535195e298a85f087906136fcd68fd35e1d7"
non_domestic_lmk_key <- "003065c69db27a109e45effc2af41d8b79de805e8963cf74edc73f1f879410ab"
display_lmk_key =  "0258793e614bca99c3c38e51395e1959e610bfc48b2e158e8fa846e6cd68ffb7"
```

```{r, message = FALSE, warning = FALSE}
energizer::odc_get_data(
  domestic_lmk_key, 
  type = "domestic",
  endpoint = "certificate"
)
```

In the same way, recommendations can also be searched: 

```{r, message = FALSE, warning = FALSE}
energizer::odc_get_data(
  domestic_lmk_key,
  type = "domestic",
  endpoint = "recommendation"
)
```

Notice that if no recommendations are found, an error message is returned.

## 📃 Paginated Search

By default, only the first page of results is returned. Searching with pagination can be done by setting  `paginate = "all"`: 

```{r, message = FALSE, warning = FALSE}
energizer::odc_search_data(
    address = "liverpool road",
    type = "domestic",
    paginate = "all", 
    size = 5000
)
```

Manual control over the pagination can be achived with:

```{r, message = FALSE, warning = FALSE}
energizer::odc_search_data(
    address = "liverpool road",
    type = "domestic",
    paginate = "manual", 
    size = 5000
)
```

In addition to the usual output, this also returns the `X-Next-Search-After` response header, which can be passed to the subsequent search via the `search_after` input argument.

## ⬇️ Bulk Download

`energizer` wraps the bulk download functionality provided by the API: 

```{r, eval = FALSE}
energizer::odc_bulk_download(
  file_name = "non-domestic-E08000025-Birmingham.zip",
  destination_path = here::here(),
  type = "certificate"
)
```

To save the `.zip` file together with the `.csv` file, set `keep_zip = TRUE`:

```{r, eval = FALSE}
energizer::odc_bulk_download(
  file_name = "non-domestic-E08000025-Birmingham.zip",
  destination_path = here::here(),
  type = "certificate",
  keep_zip = TRUE
)
```

## 🔎 Search Features

* Flexible filtering: `address`, `postcode`, `local_authority`, `dates`, `property_type`, etc.

* Smart pagination: three modes (`"none"`, `"all"`, `"manual"`)

* Result control: `max_records` and `max_pages` parameters

* Automatic type conversion: Use `local_authority` instead of `local-authority`

## ⚠️ Disclaimer

*This package is not affiliated with or endorsed by the UK Department for Levelling Up, Housing and Communities or the Open Data Communities service.*
